Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-05 paper.tex
add note about 1-indexed

The ``C'' (C row-major) format stores the concentrations of all species for a single thermochemical condition $i$  sequentially in memory, i.e., with  $[C]_{1, 1}$ in index 1, $[C]_{1, 2}$ in index 2, and so on, as shown in \cref{F:row_major}.\todo{wouldn't these start at index 0?}{}
Conversely, in the ``F'' (Fortran column-major) format the concentrations of a single species $j$ over all thermochemical states lie adjacent in memory, corresponding to storing $[C]_{1, 1}$ in index 1, $[C]_{2, 1}$ in index 2, and so on, as shown in \cref{F:column_major}.
This ordering \revise{strongly affects} the performance of SIMD\slash SIMT-vectorized algorithms, \revise{as does the device (CPU, GPU, etc.\@) and vectorization pattern in question.}

>>>>

The ``C'' (C row-major) format stores the concentrations of all species for a single thermochemical condition $i$  sequentially in memory, i.e., with  $[C]_{1, 1}$ in index 1 (\revise{using one-based index notation}), $[C]_{1, 2}$ in index 2, and so on, as shown in \cref{F:row_major}.
Conversely, in the ``F'' (Fortran column-major) format the concentrations of a single species $j$ over all thermochemical states lie adjacent in memory, corresponding to storing $[C]_{1, 1}$ in index 1, $[C]_{2, 1}$ in index 2, and so on, as shown in \cref{F:column_major}.
This ordering \revise{strongly affects} the performance of SIMD\slash SIMT-vectorized algorithms, \revise{as does the device (CPU, GPU, etc.\@) and vectorization pattern in question.}
